### 2019-09-11 initial/notes.tex
stash first attempt overplot anal

@@

We can investigate two behaviors here then, the range of permitted $\theta_f$ as
a function of $I$ (when $J_i = A_{crit}$), and the values of $\theta_f$ given
some initial mutual inclination $\hat{s} \cdot \hat{l}_p$ ($J_i = 2\pi\p*{1 -
\cos \epsilon}$ where $\epsilon$ is the initial mutual inclination).

>>>>

We can illustrate the trajectories at $\phi_{2, \epsilon}$ when turning on
$\epsilon$ by examining \lstinline{99_misc/3_trajs.py}.

@@

We can investigate the values of $\theta_f$ given some initial mutual
inclination $\hat{s} \cdot \hat{l}_p$ ($J_i = 2\pi\p*{1 - \cos \epsilon}$ where
$\epsilon$ is the initial mutual inclination). To do this, we need to understand
what the possible transitions are. When the separatrix first appears to the
final state, the transitions are $A_2 \to A_3, A_2 \to A_1, A_3 \to A_1, A_3 \to
A_2 \to A_1, A_3 \to A_3$. Let's reproduce the analytical forms of these three
areas below:

%   z0 = eta * np.cos(I)
%   chi = np.sqrt(-np.tan(q4)**3 / np.tan(I) - 1)
%   rho = chi * np.sin(q4)**2 * np.cos(q4) / (
%       chi**2 * np.cos(q4)**2 + 1)
%   T = 2 * chi * np.cos(q4) / (
%       chi**2 * np.cos(q4)**2 - 1)
%   A2 = 8 * rho + 4 * np.arctan(T) - 8 * z0 * np.arctan(1 / chi)
%   A1 = 2 * np.pi * (1 - z0) - A2 / 2
%   A3 = 2 * np.pi * (1 + z0) - A2 / 2
\begin{subequations}\label{se:}
    \begin{align*}
        z_0 &= \eta\cos I &
        \chi &= \sqrt{-\frac{\tan^3\theta_4}{\tan I} - 1},\\
        \rho &= \chi \frac{\sin^2 \theta_4\cos \theta_4}{
            \chi^2 \cos^2\theta_4 + 1} &
        T &= 2\chi \frac{\cos \theta_4}{
            \chi^2 \cos^2\theta_4 - 1},
    \end{align*}
    \begin{align}
        A_2 &= 8\rho + 4\arctan T - 8z_0 \arctan \frac{1}{\chi},\\
        A_1 &= 2\pi\p*{1 - z_0} - \frac{A_2}{2},\\
        A_3 &= 2\pi\p*{1 + z_0} - \frac{A_2}{2}.
    \end{align}
\end{subequations}
